---
title: "Co-occurrence summary for phecode : `r params$outcome_phecode` at t = `r params$t_threshold`"
format:
  html:
    code-fold: true
    page-layout: full
editor: visual
theme: flatly
params:
  outcome_phecode: "155"
  t_threshold: "5"
  data_version: "20210318"
---

```{r libraries-and-stuff, echo = FALSE}
### libraries ----------
suppressPackageStartupMessages({
  library(data.table)
  library(ggplot2)
  library(plotly)
  library(ggtext)
})

### specs ----------
out_phe <- params$outcome_phecode
t <- as.numeric(params$t_threshold)
data_vers <- params$data_version

### source plotting functions ----------
purrr::walk(
  list.files("~/Dropbox (University of Michigan)/projects/dissertation/aim_one/fn/"),
  ~source(paste0("~/Dropbox (University of Michigan)/projects/dissertation/aim_one/fn/", .x))
)
```

```{r load-data, echo = FALSE}
### load data ----------
d <- data.table::fread(
  file = paste0("~/Dropbox (University of Michigan)/projects/dissertation/aim_one/results/",
         data_vers, "/",
         paste0("X", gsub("X", "", out_phe)),
         "/mgi_X", gsub("X", "", out_phe),"_t", t,"_", data_vers, "_results.txt")
  )[, `:=` (
  phecode = gsub("X", "", phecode),
  shape = ifelse(beta > 0, "Up", "Down"),
  log10p = -log10(p_value),
  phe_num = as.numeric(gsub("X", "", phecode))
  )][]
p <- fread("~/Downloads/Phecode_Definitions_FullTable_Modified.txt", colClasses = "character")[, `:=` (
  groupnum = as.numeric(groupnum)
)]
```

```{r prep-data, echo = FALSE}
### prep data ----------
merged <- merge.data.table(
  d,
  p[, .(phecode, description, group, groupnum, color)],
  all.x = TRUE,
  by = "phecode"
)[order(groupnum, phe_num), num := 1:.N]
merged[, slide_num := num + ((groupnum - 1)*30)]
thresh <- -log10(0.05/merged[, .N])
merged[, sig := ifelse(p_value < 0.05/merged[, .N], "Significant", "Not significant")]
merged[, group := stringr::str_to_sentence(group)]
```

The following are cooccurrence analysis results for phecode `r out_phe`: `r p[phecode == out_phe, description]` in MGI at the t = `r t` year(s) threshold. `r format(merged[, .N], big.mark = ",")` phecodes were considered (at least 10 cases in time-restricted phenome). `r format(merged[sig == "Significant", .N], big.mark = ",")` phecodes reached phenome-wide significance.

### Manhattan plot of p-values

```{r}
plotlyman_log10p(data = merged, phe_data = p, outcome = out_phe)
```

### Plot of beta coefficients

```{r}
plotlyman_beta(data = merged, phe_data = p, outcome = out_phe)
```

### Table of results

```{r}
DT::datatable(merged[order(p_value), .(Phecode = phecode, Description = description, Beta = round(beta, 3), SEbeta = round(se_beta, 3), `P-value` = formatC(p_value, format = "e", digits = 2), Significant = sig, `Phecode category` = group)],
              # options = list(
              #   scrollX = TRUE,
              #   autowidth = FALSE,
              #   columnDefs = list(
              #     list(width = '75px', targets = c(1, 3, 4, 5)),
              #     list(width = '500px', targets = c(2)),
              #     list(width = '300px', targets = c(6, 7)))
              # ),
              rownames = FALSE)
```
